kableExtraTutorial

### 2017-09-17 rmd_tutorial.rmd
added notes for improving Rmd report

```{r setup, echo=FALSE}
library(knitr)
library(kableExtra)
library(ggplot2)
library(dplyr)

@@

```{r, echo=FALSE}
#save a figure of boxplots for each mouse
bb <- ggplot(MLH1_data, aes(x = mouse, y = nMLH1.foci)) + 
  geom_boxplot(data = MLH1_data, aes(fill = factor(strain), color = factor(sex) ) )

@@

>>>>

include is for blocking output messages. echo false is for silencing the code commands.
```{r setup, echo=FALSE}
library(knitr)
library(ggplot2)
library(dplyr)

@@

```{r, echo=FALSE, fig.width=3.5, fig.height = 2}
#save a figure of boxplots for each mouse
bb <- ggplot(MLH1_data, aes(x = mouse, y = nMLH1.foci)) + 
  geom_boxplot(data = MLH1_data, aes(fill = factor(strain), color = factor(sex) ) )

@@

 figure will be generated below. this is the text above that prefaces it, how and why the figure(s) are set up.
 The following figure will display the boxplots of MLH1 distributions seperated by sexes. 
```{r, MLH1 box plots, fig.width=2, fig.height=3, fig.cap="this is the figure caption"}

```
This is the text that discusses the inferences of the figures.

This is the text above the table, this will show category wide stats of MLH1 counts.
```{r}
#use kable to make tables. warning this might not work for github Rmd.
kable(my table)
```

text before the table for mouse specific tables. (make them smaller and more compact?)
```{r, mouse table}

```{r, MxF hetC plot}
